\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-10-30 analysis/paper/paper.Rmd
working on paper text

Extracted hyperspectral data for all mapped stems at NEON sites
Figure \@ref(fig:fig-spectraExtracted)
Assumed plant locations don't change over time 
Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
We performed our analysis in R [@R] with packages including neonUtilities [@neonUtilities], geoNEON [@geoNEON], neonhs [@neonhs]

>>>>

We extracted hyperspectral data for all mapped stems at NEON sites using the neonhs [@neonhs] package. 
We assumed that plant locations did not change over time.

Figure \@ref(fig:fig-spectraExtracted)

Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
We performed our analysis in R [@R] with packages including neonUtilities [@neonUtilities], geoNEON [@geoNEON], neonhs [@neonhs]
